---
title: "Final Assingment"
author: "Johanna Troberg"
date: "March 8, 2017"
output: 
  html_document: 
    theme: flatly
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    smooth_scroll: true
    code_folding: hide
    fig_width: 8
    fig_height: 6
    fig_caption: true
    
---
# Links to my repository and Data wrangling script

[jtroberg Github repository](https://github.com/jtroberg/IODS-final)

[Data wrangling](https://github.com/jtroberg/IODS-final/blob/master/data_wrangling.R)

#1. Purpose of this analysis

In this final assignment I am comparing the activities of dog and human conjugating enzymes, UDP-glucuronosyltransferases. The comparison of the individual UGT1A and 1a families are published in the paper [Troberg et al., 2015](https://jtroberg.github.io/IODS-final/#references). 

The main goal of this analysis is to see if there is any correlation or pattern visible between activities and physicochemical properties. 


```{r child = "Summary.Rmd"}
```

# 3. Analysis
In the first part of the analysis, we will just take a look at this data and see if there is any similarities between the human and canine enzymes. 

```{r child="Analysis1.Rmd"}
```


```{r child="Analysis2.Rmd"}
```


```{r child="Conclusions.Rmd"}
```
## Quarterly Results {.tabset .tabset-fade .tabset-pills}

### Our data

(tab content)

### Literature

(tab content)


# References

1. Troberg, J., et al. (2015). "Dog UDP-Glucuronosyltransferase Enzymes of Subfamily 1A: Cloning, Expression, and Activity." Drug Metabolism and Disposition 43(1): 107-118.
